newglossaryentry{dictionaryEntry}{
    name={dictionary entry},
    description={is a set of data describing a Forth word}
}

\newglossaryentry{dictionary}{
    name={dictionary},
    description={dictionary description}
}

\newglossaryentry{nameField}{
    name={name field},
    description={name field description}
}

\newglossaryentry{linkField}{
    name={link field},
    description={link field description}
}

\newglossaryentry{parameterField}{
    name={parameter field},
    description={the address of a word's parameter field. The PFA points to the parameter field.}
}

\newglossaryentry{dataField}{
    name={data field},
    description={data see parameterField}
}

\newglossaryentry{codeField}{
    name={code field},
    description={code field description}
}

\newglossaryentry{linkFieldAddress}{
    name={link field address},
    description={link field address description}
}

\newglossaryentry{nameFieldAddress}{
    name={name field address},
    description={name field address description}
}

\newglossaryentry{parameterFieldAddress}{
    name={parameter field address},
    description={parameter field address description}
}

\newglossaryentry{codePointer}{
    name={code pointer},
    description={The address of the code. Stored in a word's code field. The Code Field Address is the addresss of the code field, not the address contained within the code field.}
}

\newglossaryentry{colonWord}{
    name={colon word},
    description={Colon-defined words have parameter fields that contain pointers to code fields in other words. These pointers are Code Field Addresses.}
}

\newglossaryentry{immediateWord}{
	name={immediate word},
	description={A word that has the IMMEDIATE bit set in its dictionary
    header. Is executed during interpretation. Is executed during 
    compilation rather than compiled into a definition. Is executed during compilation and interpretation}
}

\newglossaryentry{machine-code word}{
    name={Machine-code word},
    description={A word that is directly executed by the CPU. Does not 
    call other Forth words. May exit via a jump instruction to the 
    address of NEXT or by including the contents of NEXT inline, thereby 
    avoiding a jump instruction. Examples include the words NEXT EXECUTE 
    BRANCH and EXIT .}
}

\newglossaryentry{threadedCodeWord}{
    name={threaded- word},
    description={A word that contains other Forth words. May also contain machine-code words. Exits by calling the Forth word ; .}
}

\newglossaryentry{compileWord}{
        name={compile word},
        description={description}
}

% Glossary entries (used in text with e.g. \acrfull{fpsLabel} or \acrshort{fpsLabel})
\newacronym[longplural={Central Processor Units}]{cpuLabel}{CPU}{Central Processor Unit}
